Testing atlantisom: generate census length comps for Norwegian Barents Sea Atlantis

### 2019-05-13 visualization_Rmd/NOBATrueLengthCompTest.Rmd
update with last three code blocks not evaluated

Select a single species for testing. Generating length composition for a single species should take just a few minutes to run.

@@

This code block can take hours (5+ for CCA) to run, so be prepared, but then the saved file can be read back in to have length comps for all surveyed species.

```{r allspplength, echo=TRUE}

@@

```{r loadlengthcomp, echo=TRUE}

@@

```{r moreplots, echo=TRUE}

>>>>

Select a single species for testing. Generating length composition for a single species should take just a few minutes to run. Update: for NOBA with many output timesteps, even a single species took 15-20 minutes.

@@

This code block can take hours (5+ for CCA and 18+ for NOBA) to run, so be prepared, but then the saved file can be read back in to have length comps for all surveyed species. For a normal survey query we would have only one output timestep per year, which should save some time.

```{r allspplength, echo=TRUE, eval=FALSE}

@@

```{r loadlengthcomp, echo=TRUE, eval=FALSE}

@@

```{r moreplots, echo=TRUE, eval=FALSE}
